### 2016-02-13 pdocs/thesis/bullet-plasticity.tex
f1 and f2 results

Material is steel. Density is 7800 $kg\over{m^{3}}$. Young’s modulus is 200 GPa. Yield stress is initially 400 MPa but it can be modified.

@@

\subsection{Results for single rigid body}
Timestep of 0.1 ms provides expeced results and specimen bounces hammer back.
Larger timesteps produce various kinds of unexpected results like
\begin{itemize}
\item Specimen goes trough anvil and penetrates hammer
\item Specimen moves sideways and stays on anvil. This can be seen e.g. by setting timestep to 17 ms and leaving hammer draft away.
\end{itemize}

\subsection{Results for constraint with zero limits}
This technique provides effective and stable way to simulate breaking into two objects. 
Required energy to break constraint can be controlled using
breakingImpulseThreshold.

>>>>

Material is steel. Density is 7800 $kg\over{m^{3}}$. Young’s modulus is 200 GPa. Yield stress is initially 400 MPa but it can be modified.
Coefficient of restitution can be modified and has value of 0 unless otherwise staten.

@@

\subsection{Results for single rigid body}

Timestep of 0.1 ms provides expeced results and specimen bounces hammer back as seen in figure \ref{fig:f1-ok-results}.

\begin{figure}[htb!]
\centering
\includegraphics[height=3cm]{figs/f1-18-01-1}
\includegraphics[height=3cm]{figs/f1-18-01-2}
\caption{Specimen bounces hammer back with timestep of 0.1 ms}
\label{fig:f1-ok-results}
\end{figure}

Larger timesteps produce various kinds of unrealistic results seen in figure \ref{fig:f1-nok-results}.
In these cases timestep is 17 ms. Specimen penetrates hammer and anvils.
Without draft specimen stays on anvil.

\begin{figure}[htb!]
\centering
\includegraphics[height=3cm]{figs/f1-18-17-1}
\includegraphics[height=3cm]{figs/f1-18-17-2}
\includegraphics[height=3cm]{figs/f1-18-17-3}
\caption{Results with timestep of 17 ms}
\label{fig:f1-nok-results}
\end{figure}

\subsection{Results for constraint with zero limits}
This technique provides effective and stable way to simulate breaking of brittle material 
but does not provide realistic results for ductile material as can be seen in figure \ref{fig:f3-results}.
Required energy to break constraint can be controlled using
breakingImpulseThreshold.

\begin{figure}[htb!]
\centering
\includegraphics[height=2.5cm]{figs/f3-18-01-1}
\includegraphics[height=2.5cm]{figs/f3-18-01-2}
\includegraphics[height=2.5cm]{figs/f3-18-01-3}
\caption{Specimen breaks in brittle way}
\label{fig:f3-results}
\end{figure}
